Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-03-05 article.tex
Correct figure reference

For this last point, \acp{IDE} that support \texttt{dataclass\_transform} (De
Bonte and Traut 2021) can provide a tooltip with the expected signature
(Figure~\ref{fig-composition}). This requires the use of type
annotations which play a more significant role in static type checking,
as they can help to identify errors before running the code. For
instance, to parameterize the initial conditions of variables we have to
use a \texttt{Constant}. If we try to use a \texttt{Parameter}, which
could be a time-dependent expression, it is flagged as a type error
(Figure~\ref{fig-ide}).

>>>>

For this last point, \acp{IDE} that support \texttt{dataclass\_transform} (De
Bonte and Traut 2021) can provide a tooltip with the expected signature
(Figure~\ref{fig-ide}). This requires the use of type
annotations which play a more significant role in static type checking,
as they can help to identify errors before running the code. For
instance, to parameterize the initial conditions of variables we have to
use a \texttt{Constant}. If we try to use a \texttt{Parameter}, which
could be a time-dependent expression, it is flagged as a type error
(Figure~\ref{fig-ide}).
